---
title: "Final Project Implementation"
output: github_document
---

# ================================================
# Final Project Implemenation
# ================================================

# ================================================
# Graded Challenge 1: Handle missing values using specified rules (20 points)
# ================================================

# Please do not change the variable names in this lab, as this could result in
# the autograder not registering your code correctly.

# Missing values (20 points)
# First, import all dependencies and your dataset into a new df called retail_df

````{r}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)

retail_df <- read_csv("retail_set12.csv")
```

# Next:
#1. Identify missing values: Use functions like is.na() and sum() to assess the 
# extent of missing data in each column.

# Check for missing values
```{r}
first_missing_values <- colSums(is.na(retail_df))
print(first_missing_values)
```
#2. Impute missing values: For numerical columns, use the mean or median to 
# replace NAs. For categorical columns, use the mode or a placeholder like 
# "Unknown."

# Impute missing 'UnitPrice' with the median
```{r}
retail_df$UnitPrice[is.na(retail_df$UnitPrice)] <-
  median(retail_df$UnitPrice, na.rm = TRUE)

#3. Impute missing values in the UnitPrice with median and
#   Quantity column with the mean.

# Impute missing 'Quantity' with the mean
retail_df$Quantity[is.na(retail_df$Quantity)] <- mean(retail_df$Quantity, na.rm = TRUE) # nolint


# Final Missing Values Check


first_missing_values <- colSums(is.na(retail_df))
print(first_missing_values)
```


# ================================================
# Graded Challenge 2: Customer Analysis
# (20 points)
# ================================================

#Duplicates and outliers
### Graded Challenge 2###

#1. Remove duplicates based on 'CustomerID', 'OrderDate', and 'ProductDescription' columns.
#2. Check for duplicates.
#3. Treat outliers: For the purposes of this lab, treat values outside 1.5 times the interquartile range as outliers and remove the corresponding rows. 


```{r}
print(retail_df)
```


#1. Remove duplicates based on 'CustomerID', 'OrderDate', and 'ProductDescription' columns.
```{r}
retail_df <- retail_df %>%
  distinct(CustomerID, OrderDate, ProductDescription, .keep_all = TRUE)
head(retail_df)
tail(retail_df)
```

#2. Check for duplicates.
```{r}
duplicates <- sum(duplicated(retail_df[, c("CustomerID", "OrderDate", "ProductDescription")])) # nolint
print(duplicates)
```

#3. Treat outliers: For the purposes of this lab, treat values outside 1.5 times the interquartile range as outliers and remove the corresponding rows. The solutions file will show two approaches for doing this.

#Check before removing outliers
```{r}
print(summary(retail_df))
```
```{r}
# Calculate IQR-based bounds
Q1_quantity <- quantile(retail_df$Quantity, 0.25) # nolint
Q3_quantity <- quantile(retail_df$Quantity, 0.75) # nolint
IQR_quantity <- Q3_quantity - Q1_quantity  # nolint

Q1_price <- quantile(retail_df$UnitPrice, 0.25) # nolint
Q3_price <- quantile(retail_df$UnitPrice, 0.75) # nolint
IQR_price <- Q3_price - Q1_price # nolint

# Define bounds
lower_quantity <- Q1_quantity - 1.5 * IQR_quantity # nolint
upper_quantity <- Q3_quantity + 1.5 * IQR_quantity # nolint

lower_price <- Q1_price - 1.5 * IQR_price # nolint
upper_price <- Q3_price + 1.5 * IQR_price # nolint
```

```{r}
# Identify and Remove Outliers using filter() for UnitPrice (<= 1000) and Quantity (<=2) # nolint
retail_df <- retail_df %>%
  filter(Quantity >= lower_quantity & Quantity <= upper_quantity,
         UnitPrice >= lower_price & UnitPrice <= upper_price)
```

```{r}
# View cleaned data
head(retail_df)
tail(retail_df)
```

# ================================================
# Graded Challenge 3: Standardize Date/Time Formats (20 points)
# ================================================

```{r}
head(retail_df$Address)
```


# Use str_replace_all to expand street abbreviations
```{r}
#1. Replace "Ln" with "Lane" in the Address column

retail_df <- retail_df %>%
  mutate(Address = str_replace_all(Address, "\\bLn\\b", "Lane"))


#2. Replace "Blvd" with "Boulevard" in the Address column
retail_df <- retail_df %>%
  mutate(Address = str_replace_all(Address, "\\bBlvd\\b", "Boulevard"))

head(retail_df$Address)
```

```{r}
retail_df
```
```{r}
retail_df <- retail_df %>%
  separate(Address,
           into = c("StreetNumber", "StreetName", "StreetType", "City", "State", "Zip"), # nolint
           sep = " ",
           extra = "merge",
           fill = "right")
```

```{r}
retail_df
```

```{r}
retail_df <- retail_df %>%
  separate(FullName,
           into = c("FirstName", "LastName"),
           sep = " ",
           extra = "merge")
```

```{r}
retail_df
```

# ================================================
# Graded Challenge 5: Create required calculated fields (20 points)
# ================================================
```{r}
#1.Create the Total Revenue field.
## Calculate 'TotalRevenue'
retail_df <- retail_df %>%
  mutate(TotalRevenue = UnitPrice * Quantity)
# YOUR CODE HERE - please use the field name TotalRevenue exactly and do not change it. # nolint
```

#2.Create a EuroPrice field calculating the UnitPrice in Euros (1 USD = 0.92 EUR). # nolint

## Add a column for UnitPrice in Euros. Call it EuroPrice (assuming 1 USD = 0.92 EUR) # nolint
```{r}
retail_df <- retail_df %>%
  mutate(EuroPrice = UnitPrice * 0.92)
# YOUR CODE HERE - please use the field name EuroPrice exactly and do not change it. # nolint
```
```{r}
View(retail_df)
```
```{r}
glimpse(retail_df)
```