# ================================================
# Practice Challenge 2: Reproducible Reports with R Markdown
# ================================================
# Instructions for a new file: report.Rmd

# YAML Header (copy this into your report.Rmd file)
# ---
# title: "Seattle Housing Market Analysis"
# author: "Your Full Name"
# date: "r Sys.Date()"
# output: html_document
# params:
#   zipcode: # YOUR CODE HERE
# ---

# R Markdown Setup
```{r setup, include=FALSE}
library(tidyverse)
library(plotly)
library(DT)
library(knitr)
library(broom)
library(lubridate)
cleaned_house_data <- read_csv("cleaned_house_data.csv")
```

# Step 1: Generate two plots 
# (scatter plots for sqft_living vs price and bedrooms vs price)
```{r}
# <YOUR CODE HERE>
```

# Step 2: Create and format one table for summarized price by zipcode
```{r}
# <YOUR CODE HERE>
```

# Step 3: Add narrative explanations (text chunks)
```{r}
# <YOUR CODE HERE>
```

# ================================================
# Practice Challenge 3: Interactive and Dynamic Reporting
# ================================================

# Step 1: Create an interactive plot with ggplotly()
```{r interactive_plot}
plot2 <- # <YOUR CODE HERE>
print(plot2)
```
# Step 2: Add an interactive DT table with summary by zipcode
```{r interactive_table}
# <YOUR CODE HERE>
```

# Step 4: Filter house_data based on zipcode parameter
```{r filter_by_param}
# <YOUR CODE HERE>

```

# Step 5: Knit report to HTML
# < PERFORM IN TERMINAL >